Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-17 ms.tex
finished first pass at re-write of variable f1 discussion

% check whether I545 normalization parameter is the monochromatic
% 545 GHz intensity, or if it is for the Planck bandpass
% i think it should eventually be monochromatic, since that will be
% more useful to people who want SED predictions

@@

Here $\vec{I}$ denotes the vector of observed thermal dust intensities quoted 
under the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, ..., 
$I_{3000}$). The likelihood function is given by:

@@

In order for our variable $f_1$ fits to remain sufficiently constrained 
following the introduction of a third free parameter, we enhance per-pixel S/N 
by smoothing the input maps $1^{\circ}$ FWHM, and pixelize at $N_{side}=64$. To
best constrain the model parameters in each pixel, we also include \PLANCK~100 
GHz and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at $1^{\circ}$ 
resolution.

@@

This posterior still employs the likelihood function of Equation 
\ref{equ:like}, the only difference being that $f_1$ can vary from proposal to 
proposal within each individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} 
with Equation \ref{eqn:inten}. The prior $P(T_2)$ from Equation 
\ref{equ:t2prior} remains unchanged. We adopt the following prior on $f_1$:

@@

With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
stringent prior, but we must restrict the fit from wandering with too much
freedom, as we are attempting to constrain three parameters using an SED
with only nine intensity measurements, several of which are quite noisy.

>>>>

@@

Here $\vec{I}$ denotes the vector of observed thermal dust intensities quoted 
under the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, $I_{545}$, 
$I_{857}$, $I_{3000}$). The likelihood function is given by:

@@

In order for our variable $f_1$ fits to remain sufficiently constrained 
following the introduction of a third free parameter, we enhance per-pixel S/N 
by smoothing the input maps to $1^{\circ}$ FWHM, and pixelize at $N_{side}=64$.
To best constrain the model parameters in each pixel, we also include 
\PLANCK~100 GHz and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at 
$1^{\circ}$ resolution.

@@

The likelihood here is conceptually the same as that of Equation 
\ref{equ:like}, but now depends on $f_1$, which can vary from proposal to 
proposal within each individual pixel. The other difference is that 
$\vec{\mathbf{I}}$ and $\underline{\mathbf{\tilde{I}}}$ now include 100 GHz, 
143 GHz, 140$\mu$m and 240$\mu$m, in addition to the five bands used for the 
full-resolution fits.

The prior $P(T_2)$ from Equation \ref{equ:t2prior} 
remains unchanged. We adopt the following prior on $f_1$:

@@

With $\bar{f}_1$=0.0485 (from Table \ref{tab:global}, model 2) and 
$\sigma_{\bar{f}_1}$=0.003. This is a fairly stringent prior, but we must 
restrict the fit from wandering with too much freedom, as we are attempting to 
constrain three parameters using an SED with only nine intensity measurements, 
several of which are quite noisy.
